The Perils of Exploration under Competition: \\ A Computational Modeling Approach

### 2020-07-15 journal paper/ec19paper/content/revisited.tex
fix typos

\begin{figure}[ht]
\centering
\includegraphics[scale=0.35]{ec19paper/figures/rep_distribution_nih}
\includegraphics[scale=0.35]{ec19paper/figures/ts_dg_rep_diff_nih}
\caption{Reputation scores for Needle-in-Haystack at $t=500$ (left), Reputation difference $\Thompson - \DynamicGreedy$ for Needle-in-Haystack (right).Both are smoothed using a kernel density estimate.}
\label{fig:rep_dist_nih}
%\caption*{\tiny{The plots contain a kernel density estimate of the reputation distribution at $t = 500$}}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\includegraphics[scale=0.35]{ec19paper/figures/rep_distribution_nih}
\includegraphics[scale=0.35]{ec19paper/figures/ts_dg_rep_diff_nih}
\caption{Reputation scores for Needle-in-Haystack at $t=500$ (left), Reputation difference $\Thompson - \DynamicGreedy$ for Needle-in-Haystack (right). Both are smoothed using a kernel density estimate.}
\label{fig:rep_dist_nih}
%\caption*{\tiny{The plots contain a kernel density estimate of the reputation distribution at $t = 500$}}
\end{figure}
